Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
Started new iteration on Thm 26

In order to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
In other words, we show there is no $V \in \reals^{5\times 2}$ and $w \in \reals^2$ so that $\{w : Vw = B_i\}$ is nonempty.

Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, $v_1 = (0,1)$.
In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
%In order for $\{w : Vw = B_i \}$ to be nonempty for all $i$, we assert that we must have some other $v_j$ (say, $v_2$) so that $v_2 := -v_1 = (0, -1)$.
%\jessie{I don't like this justification, but it's late and I know what I'm \emph{trying} to say... kind of.}
%This is observed since the H-rep, otherwise, would not be tight, since a line in $\reals^2$ cannot be (non-redundantly) bounded by $4$ points.
Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
\end{proof}

>>>>

We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $w \in \reals^2$ such that $\langle v_j, w \rangle = B_{ij}$.

Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
\jessie{Left off here before the reading group}
In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
\end{proof}
